---
title: "Introuction to FARS functions"
author: "N. Ames"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introuction to FARS functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package contains functions which can be used to process data downloaded from the US National Highway Traffis Safety
Administration's [Fatality Anlaysis Reporting System](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars)
(FARS).

Two functions are exposed in this package:
\itemize{
   \item \code{fars_summarize_years()}
   \item \code{fars_map_state()}
}
Examples of their use is shown in the sections below. Both functions rely on the FARS data which is included
when you install the package. Currently, data for the years 2013, 2014, and 2015 are available with the package.

## Summarize FARS data

The \code{fars_summarize_years()} function takes as input a list of years and returns a tibble containing the
number of entries in the FARS data for each month of the given years. First column
is the month, and subsequent columns for each year. If a year is invalid, then a warning message is issued.

```{r}
library(FARS)
fars_summarize_years(c(2013,2014,2015))
```

## Map fars data

The \code{fars_map_state()} function takes as input a state and a year and plots a map of
the location of the entries in the FARS database for the given state and year. The state is supplied as
an integer.

```{r}
fars_map_state(1,2013)
```

